---
output:
  pdf_document: default
  html_document:
    keep_md: yes
---
# Errata for 'Automated Data Collection with R'


Last update: `r Sys.time()`


### page 35

*Credit: Jüri Kuusik (2015-01-22)*

typo: change *"parsed_doc"* to *"parsed_fortunes$children"* 



### page 136

*Credit: Laurent Franckx (2015-02-18)*

Due to (supposedly) a bug in the RCurl package (version 1.95-4.5, bug has been reported) the following lines on page 136 give an error:

```{r, include = FALSE, cache = TRUE, eval = F}
require(RCurl)
require(stringr)
url <- "http://www.r-datacollection.com/materials/http/helloworld.html"
```

```{r, error = TRUE, cache = TRUE, eval = F}
handle <- getCurlHandle(customrequest = "HEAD")
res <- getURL(url = url, curl = handle, header = TRUE)
```


There are two workaronds at the moment. 

(1) To make the code simply run through you might give up the HTTP HEAD method used in the code above and use `customrequest = "GET"` instead:

```{r, error = TRUE, cache = TRUE, eval = F}
require(RCurl)
require(stringr)

url <- "http://www.r-datacollection.com/materials/http/helloworld.html"
res <- getURL(url = url, header = TRUE)
cat(str_split(res, "\r")[[1]])

handle <- getCurlHandle(customrequest = "GET")
res <- getURL(url = url, curl = handle, header = TRUE)
```


(2) If you want to have a working example involving HTTP HEAD method you might switch to the httr package like this:

```{r, cache = TRUE}
require(httr)

url <- "http://www.r-datacollection.com/materials/http/helloworld.html"
res <- HEAD(url)

res
res$request
res$headers[1:3]
```



### page 299--310

The website holding the UK government press releases has been altered slightly. To get the date and organisation you need to change the XPaths here...

```{r, cache = TRUE, eval = F}
library(XML)

organisation <- xpathSApply(tmp, "//dl[@data-trackposition='top']//a[@class='organisation-link']", xmlValue)
publication <- xpathSApply(tmp, "//dl[@class='primary-metadata']//abbr[@class='date']", xmlValue)
````

... and here...

```{r, cache = TRUE, eval = F}
for(i in 2:length(list.files("Press_Releases/"))){
    tmp <- readLines(str_c("Press_Releases/", i, ".html"))
    tmp <- str_c(tmp, collapse = "")
    tmp <- htmlParse(tmp)
    release <- xpathSApply(tmp, "//div[@class='block-4']", xmlValue)
    organisation <- xpathSApply(tmp, "//dl[@data-trackposition='top']//a[@class='organisation-link']", xmlValue)
    publication <- xpathSApply(tmp, "//dl[@class='primary-metadata']//abbr[@class='date']", xmlValue)
    if(length(release) != 0){
        n <- n + 1
        tmp_corpus <- Corpus(VectorSource(release))
        release_corpus <- c(release_corpus, tmp_corpus)
        meta(release_corpus[[n]], "organisation") <- organisation[1]
        meta(release_corpus[[n]], "publication") <- publication
    }
}
```

The prescindMeta() function is defunct as of version 0.6 of the tm package. The meta data can now be gathered with the meta() function.

```{r, cache = TRUE, eval = F}
meta_organisation <- meta(release_corpus, type = "local", tag = "organisation")
meta_publication <- meta(release_corpus, type = "local", tag = "publication")

meta_data <- data.frame(
    organisation = unlist(meta_organisation), 
    publication = unlist(meta_publication)
)
```

The sFilter() function is also defunct. You can filter the corpus using meta().

```{r, cache = TRUE, eval = F}
release_corpus <- release_corpus[
    meta(release_corpus, tag = "organisation") == "Department for Business, Innovation & Skills" |
    meta(release_corpus, tag = "organisation") == "Department for Communities and Local Government" |
    meta(release_corpus, tag = "organisation") == "Department for Environment, Food & Rural Affairs" |
    meta(release_corpus, tag = "organisation") == "Foreign & Commonwealth Office" |
    meta(release_corpus, tag = "organisation") == "Ministry of Defence" |
    meta(release_corpus, tag = "organisation") == "Wales Office"        
]
```

The *stringr* package also produces a hick-up with the updated version of the tm package, thus we switch to base R.

```{r, cache = TRUE, eval = F}
tm_filter(release_corpus, FUN = function(x) any(grep("Afghanistan", content(x))))
```

We need to wrap the replace function with the new content_transformer()...

```{r, cache = TRUE, eval = F}
release_corpus <- tm_map(
    release_corpus, 
    content_transformer(
        function(x, pattern){
            gsub(
                pattern = "[[:punct:]]", 
                replacement = " ",
                x
            )
        )
    )
)
```

Moreover, the tolower() function needs to be wrapped with the content_transformer()...

```{r, cache = TRUE, eval = F}
release_corpus <- tm_map(release_corpus, content_transformer(tolower))
```

The prescindMeta() function is also defunct on page 310...

```{r, cache = TRUE, eval = F}
org_labels <- unlist(meta(release_corpus, "organisation"))
```

### page 315

Since the sFilter() and prescindMeta() functions are defunct as of version 0.6 of the tm package, you need to change the code on page 315 to filter the corpus.

```{r, cache = TRUE, eval = F}
short_corpus <- release_corpus[c(
    which(
        meta(
            release_corpus, tag = "organisation"
        ) == "Department for Business, Innovation & Skills"
    )[1:20],
    which(
        meta(
            release_corpus, tag = "organisation"
        ) == "Wales Office"
    )[1:20],
    which(
        meta(
            release_corpus, tag = "organisation"
        ) == "Department for Environment, Food & Rural Affairs"
    )[1:20]
)]

table(unlist(meta(short_corpus, "organisation")))
```








